---
output:
  word_document: default
  html_document: default
---
# Lawrence Nagbe

## BAN 502 LINREG Practice

### March 7, 2023


Loading Libraries for use in data analysis

```{r}
library(tidymodels)
library(tidyverse)
library(GGally)
library(ggcorrplot)
library(gridExtra) # cleans the plot and makes it readable

```
Read into the dataset

```{r}
library(readr)
Credit <- read_csv("CreditData.csv")

```

View the structucre and summary of the dataset before analysis

```{r}
str(Credit)
summary(Credit)

```

Using ggpairs to visualize the dataset and compares correlations of the variables

```{r}
ggpairs(Credit)

```

Alternative to the the ggpairs visualization is the alpha plot for visualization purposes

```{r}
p1 = ggplot(Credit, aes(x=AnnualIncome,y=AnnualCharges)) + geom_point(alpha=0.1) #changing alpha is helpful when many points may overlap
p2 = ggplot(Credit, aes(x=HouseholdSize,y=AnnualCharges)) + geom_point(alpha=0.1)
p3 = ggplot(Credit, aes(x=YrsEdAfterHS,y=AnnualCharges)) + geom_point(alpha=0.1)
p4 = ggplot(Credit, aes(x=HrWkTV,y=AnnualCharges)) + geom_point(alpha=0.1)
grid.arrange(p1,p2,p3,p4,ncol=2)

```

Building a Regression Model with AnnualIncome to Predict AnnualCharges, using non tidymodels approach


```{r}
mod1 = lm(AnnualCharges ~ AnnualIncome, Credit)
summary(mod1) #examining the model: Is this a good model?

```
Plot the model 


```{r}
ggplot(Credit, aes(x=AnnualIncome,y=AnnualCharges)) + geom_point(alpha=0.1) + geom_smooth(method = "lm", color = "red") + theme_bw()

```


Building similar model but in Tidymodels, let's use recipe

```{r}
Credit_simple = recipe(AnnualCharges ~ AnnualIncome, Credit)
Credit_simple

```

Next, we specify the kind of model we are building

```{r}
lm_model = #gives the model type a name
  linear_reg() %>% #specifies that we are doing linear regression
  set_engine("lm") #specifies the specific type of linear tool we want to use

```


Next, we will combine the recipe and the model with a workflow 

```{r}
lm_wflow =
  workflow() %>%
  add_model(lm_model) %>%
  add_recipe(Credit_simple)

```


Next, we fit (execute) the workflow on our dataset


```{r}
lm_fit = fit(lm_wflow, Credit)

```


Finally, let's see the output of the lm_fit

```{r}
summary(lm_fit$fit$fit$fit) # three fits, the actual fits is embeded in the object

```




